\vspace{-1in} \usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{CSEC-472 Authentication Paper} \\ [14pt] \huge A Security Analysis of the Lenel BlueDiamond \\

### 2020-03-09 paper/wireframe/wireframe.tex
update wireframe to latest

\section{Preliminary Suppositions \& Implications}
\begin{itemize}
    \item A lot of research appears to be out of date in the field of lock security.
    \item This research will cover Lenel/BlueDiamond's particular implementation of BLE, which to the Author's knowledge has not been tested in an academic enviornment before.
    \item This research will extend the Wiegand research of prior by attacking newer hardware with better security features.
    \item This research has the potential to potentially affect the future design of locks from the Carrier/Lenel brand, in addition to removing security vulnerabilities in future revisions of the product.
    \item This research will provide a baseline for future work in evaluating locks from different vendors.
    \item If critical vulnerabilities are discovered, these vulnerabilities could potentially be used to take over many organizations that rely on Lenel/BlueDiamond technology for access control. 
\end{itemize}

>>>>

\section{Preliminary Suppositions \& Implications}
\begin{itemize}
    \item A lot of research appears to be out of date in the field of lock security.
    \item This research will cover Lenel/BlueDiamond's particular implementation of BLE, which to the author's knowledge has not been tested in an academic enviornment before.
    \item This research will extend the Wiegand research of prior by attacking newer hardware with better security features.
    \item This research has the potential to potentially affect the future design of locks from the Carrier/Lenel brand, in addition to removing security vulnerabilities in future revisions of the product.
    \item This research will provide a baseline for future work in evaluating locks from different vendors.
    \item If critical vulnerabilities are discovered, these vulnerabilities could potentially be used to take over many organizations that rely on Lenel/BlueDiamond technology for access control. 
\end{itemize}
